\newpage
\section{Exercises}
%
% 1.1.
%
\begin{exercise}[1.1. (a)]
    Let \( Y \) be the plane curve \( y = x^2 \) (i.e., \( Y \) is the zero set of the polynomial \( f = y - x^2 \)). Show that \( A(Y) \) is isomorphic to a polynomial ring in one variable over \( k \).
\end{exercise}
\begin{solution}
    By definition ~\ref{def:affine_coordinate_ring} of a coordinate ring, we simply have \(A(Y) = k[X, Y] / (Y - X^2)\). The isomorphism follows from the isomorphism theorem and the map \(f: k[X, Y] \rightarrow k[X]\) where we set \(f(Y) = X^2\).
\end{solution}
\begin{exercise}[1.1. (b)]
    Let \(Z\) be the plane curve \(xy = 1\). Show that \(A(Z)\) is not isomorphic to a polynomial ring in one variable over \(k\). 
\end{exercise}
\begin{solution}
    \(A(Z) = k[X, Y] / (XY - 1)\)

    We know \(A(Z)\) is an \(k\)-algebra (see remark). Consider \(f: k[X, Y] \longrightarrow k[T]\). We must have \(\ker{f} = (XY - 1)\), thus \(f(XY - 1) = 0\), so \(f(X) = 1 / f(Y)\)

    I'll think about the rigorous details later, but basically \(A(Z) \cong k[X, X^{-1}]\)
\end{solution}
\begin{exercise}[1.1. (c)]
    Let \(f\) be any irreducible quadratic polynomial in \(k[X, Y]\), and let \(W\) be the conic defined by \(f\). Show that \(A(W)\) is isomorphic to \(A(Y)\) or \(A(Z)\). Which one is it when?
\end{exercise}
\begin{solution}
    Let \(f\) be irreducible.

    \(A(W) = k[X, Y] / (f)\)
    
    isn't this kinda clear ...? I'll come back to write it down rigorously, but in general ...
\end{solution}
%
% 1.2.
%
\begin{exercise}
    Let \(V \subset \mathbb{A}^3\) be the set \(Y = \makeset{(x, x^2, x^3) \in \mathbb{A}^3}{x \in K}\).
    \begin{enumerate}
        \item Show that \(V\) is an affine variety of dimension \(1\).
        \item Find generators for the ideal \(I(V)\).
    \end{enumerate}
\end{exercise}
\begin{solution}
    An \hyperref[def:algebraic_variety]{affine variety} is an irreducible, closed subset of \(\mathbb{A}^n\) with regard to the Zariski topology.
    \begin{enumerate}
        \item We show that \(V\) is a closed subset with regard to the Zariski topology.
        \begin{enumerate}
            \item Since any algebraic set is immediately a closed subset, it is enough to show that \(V\) is the zero-locus of some subset of polynomials in \(K[X_1, \ldots, X_n]\).
            \item Consider the ideal \((Y - X^2, Z - X^3) \subset K[X, Y]\) and it's zero set \(Z(Y - X^2, Z - X^3)\).
            \item Writing out the definition of the zero set gives
            \begin{align*}
                Z(Y - X^2, Z - X^3) &= \makeset{(x, y, z) \in \mathbb{A}^3}{y - x^2 = 0, \; z - x^3 = 0} \\
                &= \makeset{(x, y, z) \in \mathbb{A}^3}{y = x^2, \; z = x^3} \\
                &= \makeset{(x, x^2, x^3) \in \mathbb{A}^3}{x \in K} \text{.}
            \end{align*}
            Thus, \(V\) is the zero set of the ideal \((Y - X^2, Z - X^3)\).
            \item Hence, by definition, \(V = Z(Y - X^2, Z - X^3)\) is an algebraic set.
        \end{enumerate}
        \item Here, we prove that \(V\) is irreducible.
        \begin{enumerate}
            \item Consider the quotient \(K[X, Y, Z] / (Y - X^2, Z - X^3)\).
            \item By substitution, we get the isomorphism
            \begin{align*}
                K[X, Y, Z] / (Y - X^2, Z - X^3) \cong K[X, X^2, X^3] = K[X] \text{.}
            \end{align*}
            \item Since \(K\) is a field it in particular an integral domain and so is \(K[X]\).
            \item Thus, \((Y - X^2, Z - X^3)\) is prime in \(K[X, Y, Z]\).
            \item With corollary \ref{cor:ideal_correspondence} we may conclude the variety \(V = Z(Y - X^2, Z - X^3)\) is irreducible.
        \end{enumerate}
        \item We show that \(V\) is of dimension \(1\).
        \begin{enumerate}
            \item By proposition 1.7, the dimension of \(V\) corresponds with the dimension of its affine coordinate ring \(A(V)\).
            \item It is
            \begin{align*}
                A(V) = K[X, Y, Z] / (Y-X^2, Z-X^3) \cong K[X].
            \end{align*}
            \item \(K[X]\) is a PID. All prime ideals are generated by irreducible elements. Thus dimension is 1.
        \end{enumerate}
    \end{enumerate}
\end{solution}


\begin{exercise}[1.3.]
    Let \(V\) be the algebraic set in \(\mathbb{A}^3\) defined by two polynomials \(X^2 - YZ\) and \(XZ - X\). Show that \(V\) is a union of three irreducible components. Describe them and find their prime ideals.
\end{exercise}
\begin{solution}
    \(V = Z(X^2 - YZ, XZ - X)\)

    If \(z = 0\), then \(x = 0\) and \(y\) can be any thing, so one irreducible component is the \(y\)-axis. This is described by \(V_1 = Z(x, z)\). \(V_1\) is irreducible because its ideal \((x, z)\) is prime because \(K[X, Y, Z] / (X, Z) \cong K[Y]\) is an integral domain.

    If \(x = 0\), then \(yz = 0\). If \(z = 0\), then see above. \(y = 0\) gives the \(z\)-axis \(V_2 = Z(x, y)\)

    If \(Z = 1\), then \(X^2 - Y = 0\), so \(X^2 = Y\). We have \(V_3 = Z(X^2 - Y, Z - 1)\). This is also irreducible because \(K[X, Y, Z]/(X^2 - Y, Z - 1) \cong K[X, Y]/(X^2 - Y) \cong K[X, X^2] = K[X]\).


    If \(Z \neq 1\), then \(X(Z - 1) = 0\) gives \(X = 0\).


    We will find the irreducible components by investigating cases.
    \begin{enumerate}
        \item Consider the subset \(V_1 = \makeset{(x, y, z) \in V}{z = 1}\).
        \begin{enumerate}
            \item If \(Z = 1\), then the polynomials reduce to
            \begin{align*}
                X^2 - YZ &\Rightarrow X^2 - Y \quad \text{and} \quad XZ - X \Rightarrow X - X \Rightarrow 0 \text{.}
            \end{align*}
            \item Thus, \(V_1\) is the zero-locus of the ideal \((X^2 - Y, Z - 1)\).
            \item This ideal \((X^2 - Y, Z - 1)\) is prime because
            \begin{align*}
                K[X, Y, Z] / (X^2 - Y, Z - 1) \cong K[X, Y]/(X^2- Y) \cong K[X, X^2] = K[X]
            \end{align*}
            is an integral domain.
            \item Hence \(V_1\) is irreducible.
        \end{enumerate}
        \item Consider the subset \(V_1 = \makeset{(x, y, z) \in V}{z \neq 1}\).
        \begin{enumerate}
            \item If \(Z \neq 1\), then we have for the second polynomial
            \begin{align*}
                XZ - X = 0 \Rightarrow X (Z - 1) = 0 \Rightarrow X = 0
            \end{align*}
            \item The first polynomial gives
            \begin{align*}
                YZ = 0
            \end{align*}
        \end{enumerate}
    \end{enumerate}
\end{solution}

    

\begin{exercise}
    If we identify \(\mathbb{A}^2\) with \(\mathbb{A}^1 \times \mathbb{A}^1\) in the natural way, show that the Zariski topology on \(\mathbb{A}^2\) is not the product topology of the Zariski topologies on the two copies of \(\mathbb{A}^1\).
\end{exercise}
\begin{solution}
    Consider \(V = Z(X^2 - Y)\).
    \begin{enumerate}
        \item We get the two projections
        \begin{align*}
            p_1(V) = \mathbb{A}^1 \quad \text{and} \quad p_2(V) = [0, \infty) \text{.}
        \end{align*}
        \item In \(\mathbb{A}^1\), the only closed sets are finite sets and \(\mathbb{A}^1\) itself.
        \item Thus \(p_2(V) = [0, \infty)\) is not closed.
    \end{enumerate}
\end{solution}
%
% 1.5.
%
\begin{exercise}[1.5.]
    Show that \(k\)-algebra \(B\) is isomorphic to the affine coordinate ring of some algebraic set in \(\mathbb{A}^n\), for some \(n\), if and only if \(B\) is a finitely generated \(k\)-algebra with no nilpotent elements.
\end{exercise}
\begin{solution}
    \begin{itemize}
        \item \(B\) isomorphic to some coordinate ring
        \item \(B\) finitely generated with no nilpotent elements
    \end{itemize}

    Let \(B\) be a \(K\)-algebra that is isomorphic to the affine coordinate ring of some algebraic set in \(\mathbb{A}^n\) for some \(n\). We show that \(B\) is finitely generated with no nilpotent elements.
    \begin{enumerate}
        \item I mean, any coordinate ring is finitely generated by \(1, X_1, X_2, \ldots, X_n\).
        \item Isn't it just if an element is nilpotent, it is in the nilradical, thus in any prime ideal and this prime ideal lies in the ideal?
        \item So let \(A / I(V)\) be a coordinate ring and assume \(x \in A / I(V)\) be nilpotent.
        \item So \(x^n \in I(V)\).
    \end{enumerate}

    Let \(B\) be a finitely generated \(K\)-algebra with no nilpotent elements. We show that \(B\) is isomorphic tp the affine coordinate ring of some algebraic set in \(\mathbb{A}^n\).
    \begin{enumerate}
        \item Firstly, let \(1, b_1, \ldots, b_n\) generate \(B\).
        \item Consider the map
        \begin{align*}
            \varphi: K[X_1, \ldots, X_n] &\rightarrow B \\
            b_i &\mapsto X_i
        \end{align*}
        \item We now need the kernel.
        \begin{align*}
            \text{ker}(\varphi) = \makeset{f \in K[X_1, \ldots, X_n]}{\varphi(f) = 0}
        \end{align*}
    \end{enumerate}
\end{solution}
%
% 1.5.
%
\begin{exercise}[1.6.]
    Any nonempty open subset of an irreducible topological space is dense and irreducible. If \(Y\) is a subset of a topological space \(X\), which is irreducible in its induced topology, then the closure \(\text{cl}(Y)\) is also irreducible.
\end{exercise}
\begin{solution}
    Let \(X\) be a irreducible topological space and let \(\mathcal{U}\) be an open subset of \(X\). We show \(\mathcal{U}\) is dense.
    \begin{enumerate}
        \item Assume \(\mathcal{U}\) does not lie dense in \(X\), i.e. \(\text{cl}(\mathcal{U}) \neq X\). In other words, there is a point \(p \in X\) with \(p \not\in \text{cl}(\mathcal{U})\).
        \item If all open neighborhoods \(\mathcal{U}_p\) of \(p\) intersects \(\mathcal{U}\), i.e. \(\mathcal{U} \cap \mathcal{V}_p \neq \varnothing\), then by definition, \(p\) must lie in the closure \(\text{cl}(\mathcal{U})\). Hence let \(\mathcal{V}_p\) be an open neighborhood of \(p\) with \(\mathcal{U} \cap \mathcal{V}_p = \varnothing\).
        \item This contradicts the irreduciblility of \(X\) hence \(\mathcal{U}\) lies dense in \(X\).
    \end{enumerate}
    We show \(\mathcal{U}\) is irreducible.
    \begin{enumerate}
        \item Assume \(\mathcal{U}\) is not irreducible, i.e. we find two open sets \(\mathcal{V}_1\) and \(\mathcal{V}_2\) with \(\mathcal{V}_1 \cap \mathcal{V}_2 = \varnothing\) and \(\mathcal{V}_1 \cup \mathcal{V}_2 = \mathcal{U}\).
        \item I mean this is obvious.
    \end{enumerate}
\end{solution}
%
%
%
\begin{exercise}[1.7.]
    Show that the following conditions are equivalent for a topological space \(X\).
    \begin{enumerate}
        \item \(X\) is Noetherian.
        \item Every nonempty family of closed subset has a minimal element.
        \item \(X\) satisfies the ascending chain condition for open subset.
        \item Every nonempty family of open subsets has a maximal element.
    \end{enumerate}
\end{exercise}
\begin{solution}
    This is simple.
\end{solution}
\begin{exercise}[1.7. (b)]
    A Noetherian topological space is quasi-compact, i.e. every open cover has a finite subcover.
\end{exercise}
\begin{solution}
    This is also just simple topology.
\end{solution}
%
%
%
\begin{exercise}[1.8.]
    Let \(V\) be an affine variety of dimension \(d\) in \(\mathbb{A}^n\). Let \(H\) be a hypersurface in \(\mathbb{A}^n\), and assume \(V \not\subset H\). Then every irreducible component of \(V \cap H\) has dimension \(d - 1\).
\end{exercise}
\begin{solution}
    I need to understand hypersurfaces first.
    \begin{enumerate}
        \item Consider any chain of \(Z_0 \subset Z_1 \subset \cdots \subset Z_k\) distinct irreducible closed subsets in \(V\). By definition, we have \(k \leq d\) for all chains.
        \item Consider now the chain
        \begin{align*}
            Z_0 \cap H \subset Z_1\cap H \subset \cdots \subset Z_k \cap H
        \end{align*}
    \end{enumerate}
\end{solution}
\begin{exercise}
    Let \(\mathfrak{a} \subset A = K[X_1, \ldots, X_n]\) be an ideal which can be generated by \(r\) elements. Then every irreducible component of \(Z(\mathfrak{a})\) has dimension \(\geq n - r\).
\end{exercise}