\documentclass{book}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

% page layout
\usepackage{geometry}
    \geometry{
        a4paper,
        total={170mm,257mm},
        left=20mm,
        top=20mm,
    }

\usepackage{amsthm}

\theoremstyle{plain}
\newtheorem{thm}{Theorem}[chapter] % reset theorem numbering for each chapter
\newtheorem{lmm}{Lemma}
\newtheorem{prps}{Proposition}

\theoremstyle{definition}
\newtheorem{exmp}[thm]{Example} % same for example numbers
\newtheorem{exr}[thm]{Exercise}

\newtheoremstyle{custom_definition}% name of the style to be used
  {\topsep} % measure of space to leave above the theorem. E.g.: 3pt
  {\topsep} % measure of space to leave below the theorem. E.g.: 3pt
  {\normalfont} % name of font to use in the body of the theorem
  {} % measure of space to indent
  {\bfseries} % name of head font
  {.\newline} % punctuation between head and body
  {\topsep}% space after theorem head; " " = normal interword space
  {\thmname{#1}\thmnumber{ #2} --- \thmnote{#3}} % Manually specify head

\theoremstyle{custom_definition}
\newtheorem{defn}[thm]{Definition} 

\usepackage{amssymb}
\usepackage{amsmath}

\usepackage{tikz}
\usepackage{tikz-cd}
\usetikzlibrary{%
  matrix,%
  calc,%
  arrows%
}

%%%%%
\newcommand{\set}[1]{\left\{\, #1 \,\right\}}
\newcommand{\makeset}[2]{\left\{\, #1 \mathrel{\mid} #2 \,\right\}}


\newcommand{\Ker}[1]{ \mathrm{Ker} \left( #1 \right) }
\newcommand{\Coker}[1]{ \mathrm{Coker} \left( #1 \right) }
\newcommand{\Imag}[1]{ \mathrm{Im} \left( #1 \right)}

\newcommand{\bigslant}[2]{{\raisebox{.2em}{$#1$}\left/\raisebox{-.2em}{$#2$}\right.}}

\newcommand{\restr}[2]{{% we make the whole thing an ordinary symbol
  \left.\kern-\nulldelimiterspace % automatically resize the bar with \right
  #1 % the function
  \vphantom{\big|} % pretend it's a little taller at normal size
  \right|_{#2} % this is the delimiter
  }}

\begin{document}
\begin{exr}
    Let \(S\) be a multiplicatively closed subset of a ring \(A\), and let \(M\) be a finitely generated \(A\)-module. Prove that \(S^{-1}M = 0\) if and only if there exists \(s \in S\) such that \(sM = 0\).
\end{exr}
\begin{proof}
    \begin{enumerate}
        \item Let \(S^{-1}M = 0\), then for all \(s \in S\) and for all \(m \in M\) we have that
        \begin{align}
            \frac{m}{s} = 0 \text{,}
        \end{align}
        or in other words, \((m, s) \equiv (0, s')\) for some \(s' \in S\).
        By definition, there exists a \(t \in S\) such that
        \begin{align}
            t(s\cdot 0 - s'm) = 0 &\iff t(0 - s'm) = 0 \\
            &\iff t s' m = 0 \text{.}
        \end{align}
        Choose \(t s'\) to be the factor and we get \(sM = 0\).
        \item If there is an \(s \in S\) such that \(sM = 0\), then we can write for all \(m \in M\) that \(s \cdot m = 0\). We have
        \begin{align}
            0 = s \cdot m = s (1 \cdot m - 1 \cdot 0)
        \end{align}
        which means again \((m, 1) \equiv (0, 1)\), hence \(S^{-1}M = 0\).
    \end{enumerate}
\end{proof}

\begin{exr}
    3.2

    Hints
    \begin{enumerate}
        \item To show that \(x \in S^{-1}\mathfrak{a}\) is contained in the Jacobson radical of \(S^{-1}A\), use Proposition 1.9., i.e.
        \begin{equation}
            x \in \mathrm{Jac}(A) \iff 1 - xy \in A^\times \text{ for all } y \in A \text{.}
        \end{equation}
        \item If \(s \in S\), then \(f(s)\) is a unit in \(S^{-1}A\).
    \end{enumerate}
\end{exr}
\begin{proof}
    We want to show that \(S^{-1} \mathfrak{a}\) is contained in the Jacobson radical of \(S^{-1} A\). Let \(x \in S^{-1}\mathfrak{a}\). From Proposition 1.9. we have that \(x \in \mathrm{Jac}(S^{-1} A)\) if and only if \(1 - xy \in (S^{-1}A)^\times\) for all \(y \in S^{-1}A\). Because \(S = 1 + \mathfrak{a}\), we can write
    \begin{equation}
        x = \frac{a_1}{1 + a_2}
    \end{equation}
    for some \(a_1, a_2 \in \mathfrak{a}\). With this, it is
    \begin{align}
        1 - xy = 1 - \frac{a_1}{1 + a_2} y = \frac{1 + a_2}{1 + a_2} - \frac{a_1 y}{1 + a_2} = \frac{1 + a_2 - a_1 y}{1 + a_2} \text{.}
    \end{align}
    Now, \(a_2 - a_1 y\) is contained in \(\mathfrak{a}\), hence the whole numerator \(1 + a_2 - a_1 y\) is contained in \(S\), and in turn, this means the whole expression is a unit in \(S^{-1}A\).

    We want to give an alternative proof to Corollary 2.5. If \(\mathfrak{a}M = M\), then \((S^{-1} \mathfrak{a}) (S^{-1} M) = (S^{-1}M)\) because modules of fractions are determined uniquely up to isomorphisms. From above, we have that \(S^{-1}\mathfrak{a}\) is contained in the Jacobson radical of \(S^{-1}A\). By Nakayama's lemma, we get \(S^{-1}M = 0\). Now applying Exercise 3.1 yields that there is a \(s \in S\) such that \(sM = 0\). Since \(S = 1 + \mathfrak{a}\), it is clearly \(s \equiv 1 \mod{\mathfrak{a}}\).
\end{proof}

\begin{exr}[3.5.i)]
\end{exr}
\begin{proof}
    Let \(S\) be saturated. We show \(A - S\) is a union of prime ideals.
    \begin{enumerate}
        \item Let \(x \in A - S\) and \(\Sigma\) be a collection of ideals that contain \(a\), but disjoint with \(S\).
        \item We show that \(\Sigma\) is nonempty has a maximal elements.
        \begin{enumerate}
            \item Consider the ideal \((a)\). Its elements are in the form \(xa\) with \(x \in A\). If \(xa \in S\), then because \(S\) is saturated, we would have \(a \in S\) which is impossible. So \((a) \cap S = \emptyset\) and we have \((a) \in \Sigma\).
            \item For each ideal chain ordered by inclusion, we can construct an upper bound via the union of the ideals in the chain. Zorn's lemma now gurantees the existence of maximal elements.
        \end{enumerate}
        \item Let \(\mathfrak{p} \in \Sigma\) be a maximal element. We show \(\mathfrak{p}\) is prime by contrapositive.
        \begin{enumerate}
            \item Let \(x, y \not\in \mathfrak{p}\).
            \item \((x) + \mathfrak{p}\) and \((y) + \mathfrak{p}\) contain \(\mathfrak{p}\) strictly.
            \item Since \(\mathfrak{p}\) was maximal in \(\Sigma\), these two ideals \((x) + \mathfrak{p}\) and \((y) + \mathfrak{p}\) are not in \(\Sigma\).
            \item But \(a\) is contained in \((x) + \mathfrak{p}\) and \((y) + \mathfrak{p}\), therefore these two ideals are not disjoint from \(S\).
            \item Let \(s \in ((x) + \mathfrak{p}) \cap S\) and \(t \in ((y) + \mathfrak{p}) \cap S\).
        \end{enumerate}
    \end{enumerate}
%
    Let \(A - S\) be a union of prime ideals. We show \(S\) is saturated.
    \begin{enumerate}
        \item Let \(xy \in S\). We show that \(x \in S\) and \(y \in S\) by contradiction.
        \begin{enumerate}
            \item Let \(xy \in S\) and assume \(x \not\in S\).
            \item The assumptions implies \(x \in A - S\).
            \item Since \(A - S\) is a union of prime ideals, there is a prime ideal \(\mathfrak{p}\) that contains \(x\).
            \item If an ideal contains \(x\), it must also contain \(xy\).
            \item So \(xy \in A - S\), or in other words, \(xy \not\in S\) which is a contradiction.
        \end{enumerate}
        \item Let \(x \in S\) and \(y \in S\), clearly \(xy \in S\) because \(S\) is multiplicatively closed.
    \end{enumerate}
\end{proof}

\begin{exr}
    Let \(\overline{S}\) be the complement of the union of prime ideals that do not meet \(S\). We show three properties of \(\overline{S}\) namely \(S \subset \overline{S}\), \(\overline{S}\) is multiplicatively closed subset and is saturated.
%
    We begin by showing \(S \subset \overline{S}\).
    \begin{enumerate}
        \item Let \(x \in S\).
        \item \(x\) is not included in the union of prime ideals that do not meet \(S\).
        \item Hence \(x \in \overline{S}\).
    \end{enumerate}
    Secondly, we show \(\overline{S}\) is a multiplicatively closed subset by contrapositive.
    \begin{enumerate}
        \item \(1\) cannot be included in any prime ideal, therefore, \(1 \in \overline{S}\).
        \item Now let \(xy \not\in \overline{S}\).
        \item \(xy\) is included in the union of prime ideals that do not meet \(S\).
        \item In particular, there must be a prime ideal \(\mathfrak{p}\) with \(xy \in \mathfrak{p}\).
        \item By definition of prime ideals, we have \(x \in \mathfrak{p}\) or \(y \in \mathfrak{p}\).
        \item So \(x\) or \(y\) is included in the union of 
    \end{enumerate}
\end{exr}

\begin{exr}[4.2]
    
\end{exr}

\end{document}