\documentclass[a4paper]{article}
\title{Topology}
\author{K}


% ---------------------------------------------------------------------
% P A C K A G E S
% ---------------------------------------------------------------------

% typography and formatting
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{exsheets}
\usepackage{environ}

% mathematics
\usepackage{amsthm} % for theorems, and definitions
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{textcomp}
%\usepackage{MnSymbol} % for \cupdot

% extra
\usepackage{xcolor}
\usepackage{tikz}

% ---------------------------------------------------------------------
% S E T T I N G
% ---------------------------------------------------------------------

% typography and formatting
\geometry{margin=3cm}

\SetupExSheets{
  counter-format = ch.qu,
  counter-within = chapter,
  question/print = true,
  solution/print = true,
}

% mathematics

% extra
\definecolor{mathif}{HTML}{0000A0} % for conditions
\definecolor{maththen}{HTML}{CC5500} % for consequences
\definecolor{mathrem}{HTML}{8b008b} % for notes

\usetikzlibrary{positioning}
\usetikzlibrary{shapes.geometric, arrows}

\theoremstyle{definition}
\newtheorem*{lemma}{Lemma}

% ---------------------------------------------------------------------
% C O M M A N D S
% ---------------------------------------------------------------------

\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\newcommand{\rank}{\text{rank}}
\newcommand{\Vol}{\text{Vol}}

\newcommand{\set}[1]{\left\{\, #1 \,\right\}}
\newcommand{\makeset}[2]{\left\{\, #1 \mid #2 \,\right\}}


\newcommand*\diff{\mathop{}\!\mathrm{d}}
\newcommand*\Diff{\mathop{}\!\mathrm{D}}

\newcommand\restr[2]{{% we make the whole thing an ordinary symbol
  \left.\kern-\nulldelimiterspace % automatically resize the bar with \right
  #1 % the function
  \vphantom{\big|} % pretend it's a little taller at normal size
  \right|_{#2} % this is the delimiter
  }}

% ---------------------------------------------------------------------
% R E N D E R
% ---------------------------------------------------------------------

\newif\ifshowproof
\showprooftrue

\NewEnviron{Proof}{%
    \ifshowproof%
        \begin{proof}%
            \BODY
        \end{proof}%
    \fi%
}%

\begin{document}
\section*{Exercise 2 c)}

\begin{proof}[Solution]
    \begin{enumerate}
        \item \(\mathcal{B}\) is a subbasis for the discrete topology. Take an arbitary subset \(\mathcal{U} \subset \mathbb{R}\). If \(\mathcal{U} = \mathbb{R}\), then we simply have
        \begin{align*}
            \mathbb{R} = \bigcup_{x \in \mathbb{R}} \{x, x + 1\}
        \end{align*}
        as \(\{x, x + 1\}\) are members of the subbasis \(\mathcal{B}\). Similary, if \(\mathcal{U} = \mathbb{R} \setminus \{y\}\) for some \(y \in \mathbb{R}\), then we have
        \begin{align*}
            \mathbb{R} \setminus \{y\} = \left( \bigcup_{\substack{x \in \mathbb{R} \\ x + 1 \neq y}} \{x, x + 1\} \right) \cup \{y - 1, y + 1\}
        \end{align*}
        because again \(\{y - 1, y + 1\}\) lies in \(\mathcal{B}\). For any other cases, notice that there are two distinct points \(y \neq z\) with \(y, z \not\in \mathcal{U}\), thus the two sets \(\{x, y\}\) and \(\{x, z\}\) are members of \(\mathcal{B}\). Therefore, we have
        \begin{align*}
            \mathcal{U} &= \bigcup_{x \in \mathcal{U}} \{x\} \\
            &= \bigcup_{x \in \mathcal{U}} \{x, y\} \cap \{x, z\} \text{.}
        \end{align*}
        In other words, every subset of \(\mathbb{R}\) is a union of finite intersections of members in \(\mathcal{B}\), thus \(\mathcal{B}\) as a subbasis generates the discrete topology.
        \item However, \(\mathcal{B}\) is not a basis of the discrete topology. Plainly, a singleton set cannot be generated from a union of elements of \(\mathcal{B}\).
    \end{enumerate}
\end{proof}

\section*{Exercise 3 b)}
Suppose \(\mathcal{B}\) is a subbasis for a topology \(\mathcal{T}\) on a set \(X\). Given another topological space \(Y\), show that a map \(f: Y \longrightarrow X\) is continuous if and only if for every \(\mathcal{U} \in \mathcal{B}\), \(f^{-1}(\mathcal{U})\) is open in \(Y\).


\begin{lemma}
    The preimage of a map is stable under arbitary unions and finite intersections.
\end{lemma}
\begin{proof}
    Let \(f: X \longrightarrow Y\) be a map, \(\{A_i\}_{i \in I}\) be a family of subsets in \(Y\), and \(A\) and \(B\) subsets in \(Y\).
    \begin{enumerate}
        \item It is plainly
        \begin{align*}
            x \in f^{-1} \left(\bigcup_{i \in I}A_i\right) &\iff f(x) \in \bigcup_{i \in I}A_i \\
            &\iff \text{there is a \(i \in I\) such that } f(x) \in A_i \\
            &\iff \text{there is a \(i \in I\) such that } x \in f^{-1}(A) \\
            &\iff x \in \bigcup_{i \in I} f^{-1}(A) \text{.}
        \end{align*}
        \item We simply have
        \begin{align*}
            x \in f^{-1}(A \cap B) &\iff f(x) \in A \cap B \\
            &\iff f(x) \in A \text{ and } f(x) \in B\\
            &\iff x \in f^{-1}(A) \text{ and } x \in f^{-1}(B)\\
            &\iff x \in f^{-1}(A) \cap f^{-1}(B) \text{.}
        \end{align*}
    \end{enumerate}
\end{proof}

\begin{proof}[Solution]
    Denote the topology of \(Y\) by \(\mathcal{S}\).

    ``\(\Rightarrow\)'': Let \(f: Y \longrightarrow X\) be continuous and fix an \(\mathcal{U} \in \mathcal{B}\). Since \(\mathcal{B}\) is subbasis, all its elements are open subsets, thus \(\mathcal{U}\) is open. Then by definition of continuous maps, the preimage \(f^{-1}(\mathcal{U})\) is also open in \(Y\). As we have fixed an arbitary \(\mathcal{U} \in \mathcal{B}\), we may conclude the desired result.

    ``\(\Leftarrow\)'': On the other hand, let for every \(\mathcal{U} \in \mathcal{B}\) the preimage \(f^{-1}(\mathcal{U})\) be open in \(Y\). Consider an arbitary open subset \(\mathcal{V} \in \mathcal{T}\). By the definition of a subbasis, \(\mathcal{V}\) is a union of finite intersection of members of \(\mathcal{B}\), i.e.
    \begin{align*}
        \mathcal{V} = \bigcup_{\alpha \in I} \left(\mathcal{U}_1^\alpha \cap \cdots \cap \mathcal{U}^\alpha_{n_\alpha} \right)
    \end{align*}
    with \(I\) being an arbitary index set, and \(n_\alpha \in \mathbb{N}\) for each \(\alpha \in I\). The preimage of \(\mathcal{V}\) therefore is
    \begin{align*}
        f^{-1}(\mathcal{V}) &= f^{-1}\left(\bigcup_{\alpha \in I} \left(\mathcal{U}_1^\alpha \cap \cdots \cap \mathcal{U}^\alpha_{n_\alpha} \right)\right) \\
        &= \bigcup_{\alpha \in I} \left( f^{-1}(\mathcal{U}_1^\alpha) \cap \ldots \cap f^{-1}(\mathcal{U}_{n_\alpha}^\alpha) \right)
    \end{align*}
    where we applied the aforementioned lemma on the last step. Now, \(f^{-1}(\mathcal{U}_i)\) are open subsets for all \(i \in \mathbb{N}\). By the definition of topological spaces, unions of finite intersections of open subsets are also open, hence \(f^{-1}(\mathcal{V})\) is open. Thus, \(f\) is continuous.
\end{proof}

\section*{Exercise 3 c)}

Now suppose \(\{(X_\alpha, \mathcal{T}_\alpha)\}_{\alpha \in I}\) is a collection of topological spaces, \((X, \mathcal{T})\) is \(\prod_{\alpha \in I} X_\alpha\) with the product topology, and the subbase \(\mathcal{B} \subset \mathcal{T}\) is taken to consist of all sets of the form
\begin{align*}
    \makeset{{x_\alpha}_{\alpha \in I}}{x_\beta \in \mathcal{U}_\beta} \subset \prod_\alpha X_\alpha
\end{align*}
for arbitary \(\beta \in I\) and \(\mathcal{U}_\beta \in \mathcal{T}_\beta\).

Show that a sequence \(\{x_\alpha^n\}_{\alpha \in I} \in X\) converges to \(\{x_\alpha\}_{\alpha \in X} \in X\) as \(n \longrightarrow \infty\) if and only if \(x^n_\alpha \longrightarrow x_\alpha\) for every \(\alpha \in I\).

\begin{proof}[Solution]
    ``\(\Rightarrow\)'': Let the sequence \(\{x_\alpha^n\}_{\alpha \in I} \in X\) converge to \(\{x_\alpha\}_{\alpha \in I} \in X\). By exercise 3 a), we have that for all subbase \(\mathcal{U} \in \mathcal{B}\) with \(\{x_\alpha\}_{\alpha \in I} \in \mathcal{U}\) it is \(\{x_\alpha^n\}_{\alpha \in I} \in \mathcal{U}\) for sufficiently large \(n\). The members of the subase was in the form
    \begin{align*}
        \left\{ \{x_\alpha\}_{\alpha \in I} \mid x_\beta \in \mathcal{U}_\beta \right\} \subset \prod_{\alpha \in I} X_\alpha \text{.}
    \end{align*}
    Thus, for each \(\alpha \in I\), we have \(x^n_\alpha \rightarrow x_\alpha\).

    ``\(\Leftarrow\)'': On the other hand, let \(x^n_\alpha\) converge to \(x_\alpha\) for every \(\alpha \in I\). By definition of convergence, we have that for every neighbourhood \(\mathcal{V}_\alpha\) of \(x_\alpha\), it is \(x^n_\alpha \in \mathcal{V}_\alpha\) for all sufficiently large \(n\). Denote the open subsets of these neighbourhoods by \(\mathcal{U}_\alpha\). Then, \(\prod_{\alpha \in I} \mathcal{U}_\alpha\) is a neighbourhood of \(\{x_\alpha\}_{\alpha \in I}\) in the product topology and also contains all \(\{x_\alpha^n\}_{\alpha \in I}\) if \(n\) is sufficiently large enough. Thus, \(\{x_\alpha^n\}_{\alpha \in I}\) converges to \(\{x_\alpha\}_{\alpha \in I}\).
\end{proof}
\section*{Exercise 7}

\begin{proof}[Solution]
    \begin{enumerate}
        \item The error is in the following part.
    
        ``which means that \(x_n\) {\color{red}cannot enter} arbitary neighbourhoods of \(x \in X\) for arbitary large values of \(n\), i.e. there exists \(N_x \in \mathbb{N}\) and an open neighbourhood of \(\mathcal{U}_x \subset X\) of \(x\) such that \(x_n \not\in \mathcal{U}_x\) {\color{red}for every} \(n \geq N_x\)''
    
        The definition of convergence of a sequence was that for every neighbourhood \(\mathcal{U} \subset X\) of \(x\) it is \(x_n \in \mathcal{U}\) for all \(n \in \mathbb{N}\) sufficiently large. Thus, if we negate the definition, we have that for every neighbourhood \(\mathcal{U} \subset X\) of \(x\) it is \(x_n \not\in \mathcal{U}\) {\color{red}for some} \(n \in \mathbb{N}\) sufficiently large.
    
        This mistakes makes the last conclusion false. The proof says ``each of these finitely many subsets contains at most finitely many terms of \(x_n\)'', but in actuality the subsets may contain infinitely many terms of \(x_n\).
        \item It sufficies to require \(X\) to be a first-countable space. Then, 
    \end{enumerate}
\end{proof}

\end{document}