We have the following tree of inclusion.
\begin{figure}[h]
    \center
    \begin{tikzpicture}[node distance=2cm and 1cm]
        \tikzstyle{box} = [draw=none, minimum width=4cm]
        \tikzstyle{arrow} = [thick,-,>=stealth]
        \node [draw=none]                 (ring of sets) {ring of sets};
        \coordinate[below=of ring of sets] (c);
        \node [box, left=of c]      (algebra of sets) {algebra of sets};
        \node [box] at (c)     (s-ring)     {\(\sigma\)-ring};
        \node [box, right=of c] (monotone class)     {monotone class};
        \node [box, below=of c]     (s-algebra)    {\(\sigma\)-algebra};
        \node [box, below=of s-algebra] (b-algebra) {Borel \(\sigma\)-algebra};
        \draw [arrow] (ring of sets) -- (algebra of sets);
        \draw [arrow] (ring of sets) -- (s-ring);
        \draw [arrow] (algebra of sets) -- (s-algebra);
        \draw [arrow] (s-ring) -- (s-algebra);
        \draw [arrow] (monotone class) -- (s-algebra);
        \draw [arrow] (s-algebra) -- (b-algebra);
    \end{tikzpicture}
\end{figure}
NOTATION GUIDE:
\begin{enumerate}
    \item \(X\) as the superset
    \item \(\mathcal{P}(X)\) is the power set of \(X\).
    \item \(A, B \in \mathcal{P}(X)\) as subsets
    \item \(\mathcal{R}, \mathcal{A} \subset \mathcal{P}(X)\) system of subsets
\end{enumerate}
%
\section{Symmetric Difference}
\begin{definition}[Symmetric difference]
    Let {\color{mathif}\(A, B\)} be {\color{mathif}sets}. The binary set operation {\color{maththen}symmetric difference} is defined as
    \begin{align}
        A \triangle B := (A \setminus B) \cup (B \setminus A) \text{.}
    \end{align}
    In other words, \(x \in A \triangle B\) implies \(x\) is either in \(A\) or \(B\), but not in both.
\end{definition}
\begin{proposition}[Properties of Symmetric Difference]
    Let \(A, B, C, X\) and \(Y\) be {\color{mathif}sets}. Moreover, let \(A_i\) and \(X_i\) be {\color{mathif}sets} with an {\color{mathif}arbitary non-empty index set} \(i \in I\). Then, the following {\color{maththen}identities} hold.
    \begin{enumerate}
        \item \( A \triangle B = (A \cup B) \setminus (A \cap B) \).
        \item \( ( A \triangle B) \triangle C = A \triangle (B \triangle C) \). (Symmetric difference is {\color{mathrem}associative}.) 
        \item \( A \triangle B = B \triangle A \). (Symmetric difference is {\color{mathrem}commutative}.)
        \item \( A \triangle \emptyset = A\) and \( A \triangle A = \emptyset\)
        \item \( (A \triangle B) \cup C = (A \cup C) \triangle (B \cup C)\).
        \item \( A \cap B = \emptyset \Rightarrow A \triangle B = A \cup B \).
        \item \( B \subset A \Rightarrow A \triangle B = A \setminus B \).
        \item \(X \cap Y = \emptyset \Rightarrow A \cap B \subset (X \triangle A) \cup (Y \triangle B) \).
        \item \( (\bigcup_{i \in I} X_i) \triangle (\bigcup_{i \in I} A_i) \subset \bigcup_{i \in I} (X_i \triangle A_i) \)
    \end{enumerate}
\end{proposition}
\begin{Proof}
    Elementary.
\end{Proof}
%
%
%
%
%
\section{Ring of Sets}
\begin{definition}[Ring of sets]
    There are two equivalent definitions. Let {\color{mathif}\(X\)} be a {\color{mathif}set} and {\color{mathif}\(\mathcal{R} \subset \mathcal{P}(X)\)} a {\color{mathif}system of subsets}. Then {\color{maththen} \(\mathcal{R}\)}  is a {\color{maththen}ring of sets over \(X\)}, if
    \begin{enumerate}
        \item the following axioms are met.
        \begin{enumerate}
            \item \(\mathcal{R} \neq \emptyset\) (\(\mathcal{R}\) is {\color{mathrem}nonempty.})
            \item \(A, B \in \mathcal{R} \Rightarrow A \setminus B \in \mathcal{R}\) (\(\mathcal{R}\) is {\color{mathrem}closed under relative complement}.)
            \item \(A, B \in \mathcal{R} \Rightarrow A \cup B \in \mathcal{R}\) (\(\mathcal{R}\) is {\color{mathrem}closed under finite unions}.)
        \end{enumerate}
        \item \((\mathcal{R}, \triangle, \cap)\) is a ring in the algebraic sense, with \(\triangle\) as addition and \(\cap\) as multiplication.
    \end{enumerate}
\end{definition}
\begin{Proof}
    We show that the two definitions above are indeed equivalent.

    \((1 \Rightarrow 2)\) Let \(\mathcal{R}\) be nonempty, closed under the relative complement, and closed under finite unions. First, consider \((\mathcal{R}, \triangle)\). Let \(A, B \in \mathcal{R}\). It is
    \begin{enumerate}
        \item (Closure under addition) \(A \cup B \in \mathcal{R}\) because \(\mathcal{R}\) is closed under finite unions. We also have \(A \cap B = A \setminus (A \setminus B) \in \mathcal{R}\) as \(\mathcal{R}\) is closed under the relative complement. From these it follows that \( A \triangle B = (A \cup B) \setminus (A \cap B) \in \mathcal{R}\) by using the closure under the relative complement again.
        \item (Associativity)
        \item (Commutativity)
        \item (Neutral element) \(\emptyset\)
        \item (Inverse element) \(A\)
    \end{enumerate}
    Therefore, \((\mathcal{R}, \triangle)\) is an abelian group. Secondly, consider \((\mathcal{R}, \cap)\). \(\cap\) is associative and commutative. The identity element is the union of all sets (does this exist??).
\end{Proof}
%
\begin{remark}
    Since we have the identity \(A \cap B = A \setminus (A \setminus B)\), the condition that \(\mathcal{R}\) is closed under the relative complement, i.e.
    \begin{align}
        A, B \in \mathcal{R} \Rightarrow A \setminus B \in \mathcal{R}
    \end{align}
    can be replaced with closure under finite intersection, therefore
    \begin{align}
        A, B \in \mathcal{R} \Rightarrow A \cap B \in \mathcal{R} \text{.}
    \end{align}
\end{remark}
%%%%%%%%%% This is already implied in the definition
% \begin{proposition}[Properties of ring of sets]
%     Let \(\mathcal{R}\) be a ring of sets. It is
%     \begin{enumerate}
%         \item \(\emptyset \in \mathcal{R}\).
%         \item \(A, B \in \mathcal{R} \Rightarrow A \triangle B \in \mathcal{R}\)
%     \end{enumerate}
% \end{proposition}
%%%%%%%%%%
\begin{example}
    Let \(X\) be a set.
    \begin{enumerate}
        \item \(\mathcal{P}(X)\) and \(\{\emptyset, X\}\) are ring of sets.
        \item \(\{\emptyset\}\) is a ring of sets.
    \end{enumerate}
\end{example}
\section{Algebra of Sets}
\begin{definition}[Algebra of sets]
    There are two equivalent definitions. Let {\color{mathif}\(X\)} be a {\color{mathif}set} and {\color{mathif}\(\mathcal{R} \subset \mathcal{P}(X)\)} a {\color{mathif}system of subsets}. Then {\color{maththen} \(\mathcal{A}\)}  is a {\color{maththen}algebra of sets over \(X\)},
    \begin{enumerate}
        \item if \(\mathcal{A}\) is a {\color{mathif}ring of sets} that contains {\color{mathif}\(X\)}, or
        \item if the following axioms are met
        \begin{enumerate}
            \item \(\mathcal{A} \neq \emptyset\) (\(\mathcal{A}\) is {\color{mathrem}nonempty.})
            \item \(A \in \mathcal{A} \Rightarrow A^c \in \mathcal{A}\) (\(\mathcal{R}\) is {\color{mathrem}closed under the absolute complement}.)
            \item \(A, B \in \mathcal{A} \Rightarrow A \cup B \in \mathcal{A}\) (\(\mathcal{R}\) is {\color{mathrem}closed under finite unions}.)
        \end{enumerate}
    \end{enumerate}
\end{definition}
%
%
%
%
%
\section{\(\sigma\)-Ring}
\begin{definition}[\(\sigma\)-Ring]
    Let \(X\) be set and \(\mathcal{R} \subset \mathcal{P}(X)\) a system of subsets. \(\mathcal{R}\) is a \(\sigma\)-ring over \(X\), if
        \begin{enumerate}
            \item \(\mathcal{R} \neq \emptyset\). (\(\mathcal{A}\) is {\color{mathrem}nonempty.})
            \item \(A, B \in \mathcal{R} \Rightarrow A \setminus B \in \mathcal{R}\) ({\color{mathrem}closed under the relative complement}.)
            \item \(A_1, A_2, A_3, ... \in \mathcal{R} \Rightarrow \bigcup_{k=1}^\infty A_k \in \mathcal{R}\) ({\color{mathrem} Closed under countable unions.})
        \end{enumerate}
\end{definition}
%
%
%
%
%
\section{Monotone Class}
\begin{definition}[Notation for Monotonous Sequence of Sets]
    % Let \((X_k)_{k \in \mathbb{N}}\) and \((Y_k)_{k \in \mathbb{N}}\) be two sequence of sets. We write
    % \begin{align}
    %     X_k \uparrow X && Y_k \downarrow Y
    % \end{align}
    % if \(X_k\) and \(Y_k\) are monotonously increasing or decreasing, i.e. \(X_k \subset X_{k + 1}\) or \(Y_k \supset Y_{k + 1}\), and
\end{definition}
\begin{definition}[Monotone class]
    Let \(\mathcal{M} \subset \mathcal{P}(\Omega)\) a system of sets and \(k \in \mathbb{N}^*\). Then, \(\mathcal{M}\) is a monotone class, if
    \begin{enumerate}
        \item Let \(X_k \in \mathcal{M}\) with \(X_k \uparrow X\), then \(X \in \mathcal{M}\).
        \item Let \(Y_k \in \mathcal{M}\) with \(Y_k \downarrow X\), then \(Y \in \mathcal{M}\).
    \end{enumerate}
    Intersection of arbitary many monotonous class is again a monotonous class. Therefore, for all \(\mathcal{E} \subset \mathcal{P}(\Omega)\) with \(\mathcal{E} \neq \emptyset\) there exists the smallest monotonous class around \(\mathcal{E}\)
    \begin{align}
        \mathcal{M}_{\mathcal{E}} := \bigcap_{\mathcal{M} \text{ is monotonous class}, \mathcal{E} \subset \mathcal{M}} \mathcal{M}
    \end{align}
\end{definition}
\begin{remark}
    All \(\sigma\)-algebras are monotone class.
\end{remark}
\begin{theorem}
    Let \(\mathcal{A} \subset \mathcal{P}(\Omega)\) an algebra of sets. Then, the following are equivalent
    \begin{itemize}
        \item \(\mathcal{A}\) is a \(\sigma\)-algebra.
        \item For \(A_k \uparrow A\), \(A \in \mathcal{A}\).
    \end{itemize}
\end{theorem}
%
%
%
%
%
\section{\(\sigma\)-Algebra}
\begin{definition}[\(\sigma\)-algebra]
    Let \(\Omega\) be set and \(\mathcal{A} \subset \mathcal{P}(\Omega)\) a system of subsets. \(\mathcal{A}\) is a \(\sigma\)-algebra over \(\Omega\), if
        \begin{enumerate}
            \item \(\mathcal{A} \neq \emptyset\).
            \item \(A \in \mathcal{A} \Rightarrow A^c \in \mathcal{A}\)
            \item \(A_1, A_2, A_3, ... \in \mathcal{A} \Rightarrow \bigcup_{k=1}^\infty A_k \in \mathcal{A}\)
        \end{enumerate}
\end{definition}
\begin{example}
    Trivial examples for the above structures.
\end{example}
\begin{definition}
    Let \(\mathcal{E} \subset \mathcal{P}(\Omega)\) be a system of sets. Define
    \begin{align}
        \mathcal{F}(\mathcal{E}) &:= \left\{ \mathcal{A} \subset \mathcal{P}(\Omega) \middle| \mathcal{E} \subset \mathcal{A}, \mathcal{A} \sigma\text{-Algebra} \right\} \\
        \left< \mathcal{E}  \right>^{\sigma} &:= \sigma(\mathcal{E}) := \bigcap_{\mathcal{A} \in \mathcal{F}(\mathcal{E})} \mathcal{A}
    \end{align}
    The first is the family of all \(\sigma\)-algebras that contain \(\mathcal{E}\).
    The second is the smallest \(\sigma\)-algebra that contains \(\mathcal{E}\).
\end{definition}
%
%
%
%
%
\section{Product Algebra??}
\begin{definition}
    Let \(\Omega_1\) and \(\Omega_1\) be sets; let \(\mathcal{R}_1 \subset \mathcal{P}(\Omega_1)\) and \(\mathcal{R}_2 \subset \mathcal{P}(\Omega_2)\) be ring of sets, and \(\Omega := \Omega_1 \times \Omega_2\). Define
    \begin{align}
        \mathcal{R} := \mathcal{R}_1 \boxtimes \mathcal{R}_2 := \left\{ \bigcup_{i=1}^m A_i \times B_i \middle| A_i \in \mathcal{R}_1, B_i \in \mathcal{R}_2, m \in \mathbb{N} \right\}
    \end{align}
    \(\mathcal{R}\) is a ring of sets over \(\Omega\).
\end{definition}
\begin{theorem}
    In above definition, if \(\mathcal{R}_1\) and \(\mathcal{R}_2\) are algebra of sets, then \(\mathcal{R}\) is a algebra of set.
\end{theorem}
\begin{theorem}
    \begin{align}
        \mathfrak{Q}(\mathbb{R}^n)
    \end{align}
    is a ring of sets.
\end{theorem}
\begin{remark}
    From \(\mathfrak{Q}(\mathbb{R}^n)\) we can construct one very important \(\sigma\)-algebra, the Borel-Algebra of \(\mathbb{R}^n\).
\end{remark}
\begin{definition}[Products of \(\sigma\)-algebras]
    Let \(\mathcal{A}_1\) and \(\mathcal{A}_2\) be \(\sigma\)-algebras on \(\Omega_1, \Omega_2\). Then, let
    \begin{align}
        \mathcal{A}_1 \otimes \mathcal{A}_2 = \sigma( \mathcal{A}_1 \boxtimes \mathcal{A}_2 )
    \end{align}
\end{definition}
\begin{example}
    \begin{align}
        \mathcal{B}(\mathbb{R}^{n+m}) = \mathcal{B}(\mathbb{R}^n) \otimes \mathcal{B}(\mathbb{R}^m)
    \end{align}
\end{example}
\begin{definition}
    Let \((X_k)_{k \in \mathbb{N}^*}\) be a sequence of sets with \(X_1 \subset X_2 \subset X_3 \subset \dots \) and \(X := \lim_{k \rightarrow \infty} := \bigcup_{k \in \mathbb{N}*} X_k\).
    Similar for monotonously decreasing.
\end{definition}

%
%
%
%
%
\section{Rectangles}
\begin{example}
    Let
    \begin{align}
        \mathfrak{Q}(\mathbb{R}) := \left\{ \bigcup_{i=1}^m [a_i, b_i)  \middle| m \in \mathbb{N}; a_i, b_i \in \mathbb{R} \right\}
    \end{align}
    be the set of all unions of finitely many right half open intervals on \(\mathbb{R}\). Then, \(\mathfrak{Q}(\mathbb{R})\) is a set of rings. Similary for the left half open sets, but not for open or closed intervals!
    \(\mathfrak{Q}(\mathbb{R})\) is neither \(\sigma\)-ring, \(\sigma\)-algebra nor an algebra of sets.
    One can generalize this to higher dimensions.
\end{example}
%
%
%
%
%
%
%
%
%
%
\section{Borel \(\sigma\)-algebra}
\begin{definition}
    Let \(\Omega\) be a set. A collection \(\mathcal{U} \subset \mathcal{P}(\Omega)\) of subsets of X is called a topology on \(X\) if it satisfies the following axioms.
    \begin{enumerate}
        \item \(\emptyset, X \in \mathcal{U}\).
        \item If \(n \in \mathbb{N}\) and \(U_1, \dots U_n \in \mathcal{U}\) then \(\bigcap_{i=1}^n U_i \in \mathcal{U}\).
        \item If \(I\) is any index set and \(U_i \in \mathcal{U}\) for \(i \in I\) then \(\bigcup_{i \in I} U_i \in \mathcal{U}\).
    \end{enumerate}
    A topological space is a pair \((\Omega, \mathcal{U})\) consisting of a set \(\Omega\) and a topology \(\mathcal{U} \in \mathcal{P}(\Omega)\).
\end{definition}
\begin{example}[Standard Topology on \(\overline{\mathbb{R}}\)]
    The set of open subsets \(\mathcal{T}\) of \(\overline{\mathbb{R}}\) is the standard topology on \(\overline{\mathbb{R}}\). Concretely, \(\mathcal{T}\) contains countable union of open intervals in \(\mathbb{R}\) and sets of the form \((a, \infty]\) or \([-\infty, b)\) for \(a, b \in \mathbb{R}\).
\end{example}
\begin{definition}[Borel algebra]
    Let \((\Omega, \mathcal{T})\) be a topological space, then \(\mathcal{B}(\Omega) := \sigma(\mathcal{T})\) is the Borel \(\sigma\)-algebra of \(\Omega\). The elments of \(\mathcal{B}\) are called Borel (measurable) sets.
    There are many ways to generate this algebra.
\end{definition}
\begin{theorem}
    Let \((\Omega, \mathcal{T})\) be a topological space. Then the following holds.
    \begin{enumerate}
        \item Every closed subset \(F \subset \Omega\) is a Borel set.
        \item Every countable union \(\bigcup_{i=1}^\infty F_i\) of closed subsets \(F_i \subset \Omega\) is a Borel set.
        \item Every countable intersection \(\bigcap_{i=1}^\infty F_i\) of open subsets \(F_i \subset \Omega\) is a Borel set.
    \end{enumerate}
\end{theorem}
\begin{theorem}
    It is
    \begin{align}
        \mathcal{B}(\mathbb{R}^n) = \sigma(\mathfrak{Q}(\mathbb{R}^n))
    \end{align}
    Moreover, define
    \begin{align}
        \mathfrak{Q}_{\mathbb{Q}}(\mathbb{R}^n) := \left\{ \bigcup_{i=1}^m [a_{1, i}, b_{1, i}) \times \dots [a_{n, i} \times b_{n, i}) \middle| m \in \mathbb{N}; a_{\nu, i}, b_{\nu, i} \in \mathbb{Q}; \nu = 1, \dots, n \right\}
    \end{align}
    the ring of sets of finite unions of quadern with rational edge points. Then, we even have
    \begin{align}
        \mathcal{R}(\mathbb{R}^n) = \sigma( \mathfrak{Q}_{\mathbb{Q}} (\mathbb{R}^n))
    \end{align}
\end{theorem}
\begin{lemma}
    Open subsets \(U \subset \mathbb{R}^n\) are disjoint union of countably many right half open dices with edge points in \(\mathbb{Q}^n\)
\end{lemma}
%
%
%
\section{Exercises}
\begin{question}
    Let \(X\) be a nonempty set and for all \(1 \leq i \leq m\) with \(m \in \mathbb{N}\) let \(A_i \subset X\) be a finite amount of subsets. Set
    \begin{align}
        S := A_1 \triangle A_2 \triangle \dots \triangle A_m \text{.}
    \end{align}

    Because of the associative property of the symmetric difference, \(S\) is uniquely defined regardless of the order of the operations.

    Show that \(x \in X\) belongs to \(S\) if and only if \(x\) belongs to an odd number of sets \(A_k\), i.e. when the number of indices \(k \in \{1, 2, \dots, m\}\) with \(x \in A_k\) is odd.
\end{question}
\begin{solution}
    % trivial 
\end{solution}
%
%
%
\begin{question}
    Let \(X\) be a nonempty set and \(R := \{f: X \rightarrow \mathbb{F}_2\}\) where \(\mathbb{F}_2 = \{0, 1\}\) is a field of two elements equipped with the common addition and the common multiplication. Moreover, define the operations
    \begin{align}
        (f \oplus g)(x) &:= f(x) + g(x) \\
        (f \otimes g)(x) &:= f(x) \cdot g(x) \text{.}
    \end{align}
    Show the following statements.
    \begin{enumerate}
        \item \((R, \oplus, \otimes)\) is a commutative ring with the identity element.
        \item The map \(\mathcal{P}(X) \rightarrow R, A \mapsto \chi_A\) that maps a subset \(A \subset X\) to its characteristic function is bijective.
        \item For all \(A, B \in \mathcal{P}(X)\) we have
        \begin{align}
            \chi_{A \triangle B} = \chi_A \oplus \chi_B && \chi_{A \cap B} = \chi_A \otimes \chi_B \text{.}
        \end{align}
        \item Conclude from the statements above that \(\mathcal{P}(X)\) is isomorphic to \(R\) as a ring with \(\triangle\) as its addition and with \(\cap\) as its multiplication.
        \item A subset \(\mathcal{R} \subset \mathcal{P}(X)\) is a ring of sets if and only if \(\mathcal{R}\) is a subring of \(\mathcal{P}(X)\) with respects to the ring structure defined above.
    \end{enumerate}
\end{question}
\begin{solution}
    
\end{solution}
%
%
%
\begin{question}
    %PRAESENZUEBUNG 2.1
\end{question}
%
%
%
\begin{question}
    %PREASENZUEBUNG 2.2
\end{question}
% UEBUNGSBLATT 2
\begin{question}
    Show explicitly that the following subsets generate the same \(\sigma\)-algebra on \(\mathbb{R}\).
    \begin{align}
        \mathcal{E}_1 &:= \{(a, b) \mid a, b \in \mathbb{R}, \, a \leq b\} &         \mathcal{E}_2 &:= \{[a, b) \mid a, b \in \mathbb{Q}, \, a \leq b\} \\
        \mathcal{E}_3 &:= \{[a, b) \mid a, b \in \mathbb{R}, \, a \leq b\} &
        \mathcal{E}_4 &:= \{(-\infty, b) \mid a, b \in \mathbb{Q}, \, a \leq b\}
    \end{align}
\end{question}
\begin{solution}
    We want to proof
    \begin{align}
        \sigma (\mathcal{E}_1) = \sigma (\mathcal{E}_2) = \sigma (\mathcal{E}_3) = \sigma (\mathcal{E}_4) \text{.}
    \end{align}
    We will do this by showing four inclusions. In each step, our goal is to show that an arbitary interval from the generator of the superset is included in the \(\sigma\)-algebra of the subset.
    \begin{enumerate}
    \item First we show \(\sigma (\mathcal{E}_1) \subset \sigma (\mathcal{E}_2)\). Fix \(a, b \in \mathbb{Q}\) with \(a \leq b\) and consider the interval \([a, b)\). If \(a = b\), then the interval is empty and \([a, b) = \varnothing \in \sigma (\mathcal{E}_1)\) immediately. Now let \(x, y \in \mathbb{R}\) with \(x < y < a\). The set \((x, a)^c \cap (y, b)\) is included in \(\sigma (\mathcal{E}_1)\) as \(\sigma\)-algebras are closed under absolute complements and intersections. We also have
    \begin{align}
        (x, a)^c \cap (y, b) = \left( (-\infty, x] \cup [a, \infty] \right) \cap (y, b) = [a, b) \text{.}
    \end{align}
    Therefore, it follows that \([a, b) \in \sigma (\mathcal{E}_1) \) and hence \(\sigma (\mathcal{E}_1) \subset \sigma (\mathcal{E}_2)\).
    \item Next, we show \( \sigma (\mathcal{E}_2) \subset \sigma (\mathcal{E}_3) \). As before, fix \(a, b \in \mathbb{R}\) with \(a \leq b\) and consider the interval \([a, b)\). If this interval is empty, it is included in \(\sigma (\mathcal{E}_2)\), so assume \(a < b\). Let \((a_k)_{k \in \mathbb{N}}\) and \((b_k)_{k \in \mathbb{N}}\) sequences in \(\mathbb{Q}\) with \(a < a_k\) and \(b_k < b\) and with \(a\) and \(b\) as their limits respectively. Since a \(\sigma\)-algebra is closed under countable unions, \(\bigcup_{k=1}^\infty [a_k, b_k)\) is included in \(\sigma (\mathcal{E}_2)\), but we also have
    \begin{align}
        \bigcup_{k=1}^\infty [a_k, b_k) = \lim_{k \rightarrow \infty} [a_k, b_k) = [a, b)
    \end{align}
    \end{enumerate}
\end{solution}